---
title: "Taiwan Universities: Exploratory Analysis"
author: "José Donado"
date: '`r Sys.Date()`'
output: html_document
number_sections: true
---

# Description

This R Markdown presents a brief exploratory analysis of the list of universities and colleges available to study in Taiwan. The main objective is to determine how many of them exist, how many of the universities offer scholarships and how many of them each university/college offers. It is also expected to know what institutions type there are and choose 10 that are of my interest.

## Dataset and directory

```{r}
# directoryyyy
setwd("C:/Users/josep/Downloads")

# data source
library(readxl)
df <- read_excel("University_or_College_381b08.xlsx")

## LIBRARIES
library(tidyverse)
library(dplyr)
library(skimr)
```

# Exploratory Data Analysis (EDA)

## Questions?

1.  Is there a relation between location and scholarship?
2.  How many universities offer scholarship?
3.  Is higher program related with better education?
4.  Count of Unis and Colleges.
5.  what type of institutions there are?
6.  how many unis per region?
7.  quantity of programs and scholarships per region (in a table).
8.  What is the dispersion, mean, and other statistical parameters of the variable Program, Scholarship?

> Far better an approximate answer to the right question, which is often vague, than an exact answer to the wrong question, which can always be made precise.

> > — John Tukey

## About the dataset

```{r}
glimpse(df)

```

140 observations, 7 variables: doubles: Program, Scholarship chr: `School Name`, region, etc...

```{r}
library(skimr)
skim(df)
```
There are 140 universities, 5 regions, 4 types of institutions.

I need to make the regions and types of institutions factors...
```{r}
df$region <- as.factor(df$region)
df$`Institution Type` <- as.factor(df$`Institution Type`)

```


## Answers to questions
1.  Is there a relation between location and scholarship?

```{r}
df %>%
  group_by(region) %>%
  summarise(Total_Scholarship=sum(Scholarship, na.rm = TRUE)) %>%
  arrange(desc(Total_Scholarship))


```
```{r}
library(dplyr)

df %>%
  group_by(region) %>%
  summarise(
    Total_Scholarships = sum(Scholarship, na.rm = TRUE),    # Adds up all scholarships (assuming 1=Yes)
    Total_Schools = n_distinct(`School Name`),              # Counts unique universities
    Scholarships_Per_School = Total_Scholarships*100 / Total_Schools  # Calculates the ratio
  ) %>%
  arrange(desc(Scholarships_Per_School))
```
Eastern Taiwan has a bigger proportion of scholarships per amount of schools, followed by the northern region. Around half of the schools in southern and central Taiwan offer scholarships. 

Withouth the need to do a further analysis it is conspicuous that there is a relation with region and quantity of scholarships since the proportion is statistically different between each region. 

I would like to be in a region wich has a higher probability of offering a scholarship, not because I will apply to them, but because I hope there are more students that have been granted with one that I can relate to.

2.  How many universities offer scholarship?

```{r}

df %>%
  group_by(region) %>%
  summarise(
  
    Total_Schools = n_distinct(`School Name`),
    
    
    Number_Scholarship = n_distinct(`School Name`[Scholarship != 0]),
    Percentage_of_Scholarships_region = Number_Scholarship*100 / Total_Schools
  ) %>%
  arrange(desc(Percentage_of_Scholarships_region))

```
Just 18 schools from the North offer scholarships. There are more schools that offer scholarships in Central and Southern Taiwan in proportion to the amount of scholarships they have.

3.  Is higher program related with better education?

Can't tell with this data. I need to investigate with other aproximation.
4.  Count of Unis and Colleges.

```{r}
df %>%
  group_by(region) %>%
  count(region) %>%
  arrange(desc(n))

ggplot(data = df, aes(x = reorder(df$`Institution Type`, df$`Institution Type`, function(x) length(x)))) +
  
  geom_bar() +
  

  geom_text(
    stat = "count",                 
    aes(label = after_stat(count)), 
    vjust = -0.5                    
  )


```
There are 59 private technical universities and colleges, 34 private Unis, 32, national (public) and 15 national technical.

5.  what type of institutions there are?

```{r}
summary(df$`Institution Type`)
```



6.  how many unis per region?



```{r}
df %>%
  group_by(region) %>%
  count(region) %>%
  arrange(desc(n))

ggplot(data = df, aes(x = reorder(region, region, function(x) length(x)))) +
  
  geom_bar() +
  

  geom_text(
    stat = "count",                 
    aes(label = after_stat(count)), 
    vjust = -0.5                    
  )

```
The majority of unis are in Northern Taiwan, followed by Southern and Central. There are only 7 left in the East and Offshore Islands, something that suggests an educational oligarchy. 

7.  quantity of programs and scholarships per region (in a table).

```{r}
df %>%
  group_by(region) %>%
  summarise(
  
    Total_Schools = n_distinct(`School Name`),
    
    
    Number_Scholarship = n_distinct(`School Name`[Scholarship != 0]),
    
    Programs = sum(Program)
  ) %>% arrange(Programs)
```
Northern Taiwan offers the biggest amount of programs, which surpasses by 543 the next in the list: Southern Taiwan with 815. 

This gives me a general grasp of what I'm going to find answering the next question:


8.  Total Programs by Institution Type

```{r}

df %>%
  group_by(`Institution Type`) %>%
  summarise(
    Total_Programs = sum(Program, na.rm = TRUE)
  ) %>%
  arrange(desc(Total_Programs)) 

ggplot(df, aes(x= `Institution Type`, y = Program)) +
  geom_col(fill='black') + 
  
  labs(title='Total Programs by Institution Type', x='Type of Institution', y = 'Total Programs')
```

National univerisites offer the most amount of programs (probably more diverse). Private universities are then, but technical seem to have much less.

9. What is the dispersion, mean, and other statistical parameters of the variable Program, Scholarship?

```{r}
df %>%
  summarise(
    # --- Program Statistics ---
    Avg_Program = mean(Program, na.rm = TRUE),
    Median_Program = median(Program, na.rm = TRUE),
    SD_Program = sd(Program, na.rm = TRUE),       # Measure of Dispersion
    Var_Program = var(Program, na.rm = TRUE),     # Variance

  )

df %>%
  summarise(

    
    # --- Scholarship Statistics ---
    Avg_Scholarship = mean(Scholarship, na.rm = TRUE),
    Median_Scholarship = median(Scholarship, na.rm = TRUE),
    SD_Scholarship = sd(Scholarship, na.rm = TRUE),
    Var_Scholarship = var(Scholarship, na.rm = TRUE)
  )
```
The average amount of programs is 20 per univeristy but there is great dispersion with some having 0 programs, and since the median is inferior to the average it skews the program's distribution to the left. The median is a more representative statistics in this case. 

On the other hand, the mayority of universities don't offer a scholarship, but there is a good chance that there will be a scholarship in one of the universities in the Norht, East or South.


